Price of Anarchy for Mean Field Games

### 2018-07-19 PoA.tex
update prop 5

\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$ then 
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	First, we consider $\bar{b}_2 \to 0$. For every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.

@@

	Let $u^{\bar{b}_2 \to 0}:[0,T]\to \mathbb{R}$ be the solution to the limiting Riccati equation:
	\begin{equation}
	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} +B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{r \to \infty} = D^{\bar{b}_2 \to 0}_u,
	\end{equation}
	which we recall has an explicit solution. It is easy to show that for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}u^{\bar{b}_2}_t=u^{\bar{b}_2 \to 0}_t$. Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small enough $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}. Let $\epsilon>0$. Then there is a $\bar{b}^*_2$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$. We have the following two inequalities for $\bar{b}_2<\bar{b}^*_2$ and $\forall t \in [0,T]$:
		\begin{IEEEeqnarray*}{rl}
			&\left\vert (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{+,\bar{b}_2}_u) - (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{-,\bar{b}_2}_u) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u) (T-t)} \right\vert\\
			&\leq  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} \\
			&< \infty,
		\end{IEEEeqnarray*}
		and 
		\begin{IEEEeqnarray*}{rl}
			& \left\vert ( -\delta^{-,\bar{b}_2}_u + D^{u,\bar{b}_2} B^{\bar{b}_2} ) + (\delta^{+,\bar{b}_2}_u - D^{u,\bar{b}_2} B^{\bar{b}_2} ) e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right\vert \\
			&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
			&>  0.
		\end{IEEEeqnarray*}
		Thus, we can deduce that:
		\begin{IEEEeqnarray}{rCl}
			\vert u_t^{\bar{b}_2} \vert  &\leq& c_2,\ \forall t \in [0,T],\ \bar{b}_2<\bar{b}^*_2.  \nonumber
		\end{IEEEeqnarray}
	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2 \to 0}_t$ is uniformly bounded over $t \in [0,T]$ for small enough $\bar{b}_2$.

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{\bar{b}_2,MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{\bar{b}_2 \to 0,MFG}_t>0.$$
	Moreover, $\bar{x}_t^{\bar{b}_2,MFG}$ is uniformly bounded over $\bar{b}_2<\bar{b}^*_2$ and $t \in [0,T]$, i.e. 
	$$ \vert \bar{x}^{\bar{b}_2,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + c_1 c_2) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$

@@

	Now, for the case when $\bar{b}_2 \to \infty$,  we have $\lambda^{\bar{b}_2} \to 0$
	and $B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0$. It can be shown that:
	$$\lim_{\bar{b}_2 \to \infty}C^{u,\bar{b}_2}\sqrt{b_2+\bar{b}_2}=0,$$
	and
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm \delta^{\bar{b}_2 \to \infty},$$
	and therefore,
	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty,$$
	$$\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
	Also, note from the assumptions $q_T+\bar{q}_T(1-s_T)>0$ and $q_T+\bar{q}_T(1-s_T)^2>0$, we have $D^u>0$ and $D^w>0$. From equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
	\begin{equation*}
	\begin{split}
	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t =& \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\infty, \bar{b}_2} (r + \bar{r}(1-\bar{s})^2) ,
	 \end{split} 
	\end{equation*}
	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) }{r+ \bar{r}(1-\bar{s})} (q_T + \bar{q}_T(1-s_T))$. 
	Thus, for $t \in [0,T)$, we have:
	\begin{equation*}
	B^{\bar{b}_2} u^{\bar{b}_2}_t=\frac{\sqrt{b_2+\bar{b}_2}}{r+\bar{r}(1-\bar{s})^2} \cdot (b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{}\infty.
	\end{equation*}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we deduce:
	$$\lim_{\bar{b}_2 \to \infty} \bar{x}_t^{\bar{b}_2 \to \infty,MFG} = 0,\ \forall t \in (0,T]. $$	
	Similarly, we can show that for $t \in [0,T)$:
	\begin{equation*}
	\begin{split}
	(b_2 + \bar{b}_2) w^{\bar{b}_2}_t =&\frac{ \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) - \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)} }\\
	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w},
	\end{split}
	\end{equation*}
	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$ and therefore $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2}=0$.

@@

	Hence, from Proposition \ref{prop:diff_SC} and by the bounded convergence theorem, we deduce:
	$$ \lim_{\bar{b}_2 \to \infty} \Delta SC^{\bar{b}_2} =  \frac{1}{2(r+ \bar{r}(1-\bar{s})^2)} \int_0^T \lim_{\bar{b}_2 \to \infty}\left[ \left( \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} u^{\bar{b}_2}_t }{\sqrt{b_2 + \bar{b}_2}} - (b_2 + \bar{b}_2)w^{\bar{b}_2}_t \right)^2 \cdot \left(\bar{x}_t^{\bar{b}_2,MFG} \right)^2\right] dt = 0.$$	
	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$. Clearly we also have $0 \leq w^{\bar{b}_2 \to \infty}_0 < \infty$. Thus,
	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV,\bar{b}_2} <\infty.$$
	Therefore, we conclude that:
	$$ \lim_{\bar{b}_2 \to \infty} PoA^{\bar{b}_2} = 1.$$
\end{proof}

>>>>

%proposition 5
\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$
	then 
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	First, we consider $\bar{b}_2 \to 0$. For every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.

@@

	Let $u^{\bar{b}_2 \to 0}:[0,T]\to \mathbb{R}$ be the solution to the limiting Riccati equation:
	\begin{equation}
	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} +B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{r \to \infty} = D^{\bar{b}_2 \to 0}_u,
	\end{equation}
	which we recall has an explicit solution. It is easy to show that for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}u^{\bar{b}_2}_t=u^{\bar{b}_2 \to 0}_t$. Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small enough $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}. Because $\bar{b}_1 > 0$, we have $A^u < 0$. For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$. We have the following two inequalities for all $\bar{b}_2<\bar{b}^*_2$ and for every $t \in [0,T]$:
		\begin{IEEEeqnarray*}{rl}
			&\left\vert (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{+,\bar{b}_2}_u) - (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{-,\bar{b}_2}_u) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u) (T-t)} \right\vert\\
			&\leq  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} \\
			&< \infty,
		\end{IEEEeqnarray*}
		and 
		\begin{IEEEeqnarray*}{rl}
			& \left\vert ( -\delta^{-,\bar{b}_2}_u + D^{u,\bar{b}_2} B^{\bar{b}_2} ) + (\delta^{+,\bar{b}_2}_u - D^{u,\bar{b}_2} B^{\bar{b}_2} ) e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right\vert \\
			&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
			&>  0.
		\end{IEEEeqnarray*}
		Thus, we can deduce that:
		\begin{IEEEeqnarray}{rCl}
			\vert u_t^{\bar{b}_2} \vert  &\leq& c_2,\ \forall t \in [0,T],\ \bar{b}_2<\bar{b}^*_2.  \nonumber
		\end{IEEEeqnarray}
	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2}$ is uniformly bounded over $[0,T]$ for small enough $\bar{b}_2$.

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{\bar{b}_2,MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{\bar{b}_2 \to 0,MFG}_t>0.$$
	Moreover, $\bar{x}^{\bar{b}_2,MFG}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$, i.e. 
	$$ \vert \bar{x}^{\bar{b}_2,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + c_1 c_2) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$

@@

	Now, for the case when $\bar{b}_2 \to \infty$,  we have $\lambda^{\bar{b}_2} \to 0$
	and $B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0$. It can be shown that:
	$$\lim_{\bar{b}_2 \to \infty}C^{u,\bar{b}_2}\sqrt{b_2+\bar{b}_2}=0,$$
	and
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm \delta^{\bar{b}_2 \to \infty},$$
	and therefore,
	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty,$$
	$$\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
	Also, note from the assumptions $q_T+\bar{q}_T(1-s_T)>0$ and $q_T+\bar{q}_T(1-s_T)^2>0$, we have $D^u>0$ and $D^w>0$. From equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
	\begin{equation*}
	\begin{split}
	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t =& \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\bar{b}_2 \to \infty} (r + \bar{r}(1-\bar{s})^2),
	 \end{split} 
	\end{equation*}
	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) }{r+ \bar{r}(1-\bar{s})} (q_T + \bar{q}_T(1-s_T))$.

	Let's denote $(b_2 + \bar{b}_2)^{\frac{1}{2}} = p$ and $f(p) = p^3 u_{t_2}^{\bar{b}_2}$, then we know that $f(p) \xrightarrow[p\to \infty]{} \delta^{\bar{b}_2 \to \infty} (r + \bar{r}(1- \bar{s})^2) := c_3 > 0$.

	%Nicolas: Mean Value theorem
	Since $u_t^{\bar{b}_2}$, $w_t^{\bar{b}_2}$ and $\bar{x}_t^{\bar{b}_2,MFG}$ are continuous over $[0,T]$, we have then the functions $t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{\bar{b}_2,MFG} )^2 ds$ are continuous over $[0,T]$ and differentiable over $(0,T)$. Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed times $0< t_2 < t_1 < T$ such that
	\begin{IEEEeqnarray}{rCl}
		\Delta SC &=& \frac{1}{2} B^{\bar{b}_2} \int_0^T (u_t- w_t)^2 (\bar{x}_t^{\bar{b}_2,MFG} )^2 dt  \nonumber \\
		&=& \frac{1}{2} B^{\bar{b}_2}  (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 (\bar{x}_{t_1}^{\bar{b}_2,MFG} )^2  \cdot T \nonumber \\
		&=& \frac{T  B^{\bar{b}_2} }{2} \cdot (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \mathbb{E}[\xi]^2 e^{ 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{\bar{b}_2} u_s^{\bar{b}_2} ds } \nonumber \\
		&=&  \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot \left[ (b_2 + \bar{b}_2) e^{- B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1}  \right]^2 \nonumber \\
		&=& \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \left(p^2 e^{- \kappa_2 p f(p)} \right)^2
	\label{eq:delta_SC_b_2_bar_infty}
	\end{IEEEeqnarray}
	where $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$ (or $p$).

	Our next step is to show that $p^2 e^{- \kappa p f(p) } $ tends towards $0$ when $p \to \infty$. This can be done fairly easy. Since $f(p) \to c_3 >0$, there exists an $\epsilon > 0 $ such that $c_3 - 2 \epsilon >0$ and a constant $p^* := p^*(\epsilon)>0$ so that for all $p \geq p^*$ we have $\vert f(p) - c_3 \vert < \epsilon$. Then $f(p) - (c_3 - 2\epsilon) > \epsilon$ and 
	\begin{equation*}
	\begin{array}{rll}
		p^2 e^{- \kappa p f(p)} &=& e^{- \kappa p (f(p) - c_3 + 2\epsilon) }\cdot e^{- \kappa  (c_3 - 2 \epsilon) p + 2 \ln p } \\
		& \leq & e^{- \kappa p^* \epsilon} \cdot e^{- \kappa (c_3 - 2 \epsilon) p + 2 \ln p} 
	\end{array}
	\end{equation*}
	Then, for any $\epsilon_1>0$, we can choose $p$ large enough, say $p \geq p^*_1 > p^*$, so that
	\begin{equation}
		p^2 e^{-\kappa p f(p)} \leq \epsilon_1.
	\label{eq:limit_p_f(p)}
	\end{equation}

 	Now, in order to show that $\Delta SC$ tends to $0$, we need to bound the terms $u_{t_1}^{\bar{b}_2}$ and $w_{t_1}^{\bar{b}_2}$ for large enough $\bar{b}_2$. We observe that for any fixed $t_1 \in (0,T_1)$, we have
 	$$ (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_1}^{\bar{b}_2} \xrightarrow[\bar{b}_2 \to \infty]{} c_3, $$
 	then for any $\epsilon >0$ there exists a $\bar{b}_2^* > 1$ such that for any $\bar{b}_2 \geq \bar{b}_2^*$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_1}^{\bar{b}_2} \leq c_3 + \epsilon$. Thus, for any $\bar{b}_2 \geq \bar{b}_2^*$ we deduce
 	$$ u_{t_1}^{\bar{b}_2} \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
 	$$

 	Idem, we can show that for $t_1 \in [0,T)$:
	\begin{equation*}
	\begin{split}
	(b_2 + \bar{b}_2) w^{\bar{b}_2}_{t_1} =&\frac{ \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) - \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T- t_1)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t_1)} }\\
	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w} := c_4 >0,
	\end{split}
	\end{equation*}
	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$. Thus $w_{t_1}^{\bar{b}_2}$ can also be bounded $c_4 + \epsilon$ for large enough $\bar{b}_2$.

	Hence, together with the equation (\ref{eq:delta_SC_b_2_bar_infty}) and  (\ref{eq:limit_p_f(p)}), we obtain that for any $\epsilon > 0$, there exists a $\bar{b}_2^*$ large enough so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have
	$$ \Delta SC \leq \kappa_1 (c_3 + c_4 + 2 \epsilon)^2 \epsilon,$$
	which implies that 
	$$\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.$$

% error in the proof of proposition 5
\begin{comment}

	%Thus, for $t \in [0,T)$, we have:
	%\begin{equation*}
	%B^{\bar{b}_2} u^{\bar{b}_2}_t=\frac{\sqrt{b_2+\bar{b}_2}}{r+\bar{r}(1-\bar{s})^2} \cdot (b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{}\infty.
	%\end{equation*}
	%From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we deduce:
	%$$\lim_{\bar{b}_2 \to \infty} \bar{x}_t^{\bar{b}_2 \to \infty,MFG} = 0,\ \forall t \in (0,T]. $$

@@

	Hence, from Proposition \ref{prop:diff_SC} and by the bounded convergence theorem, we deduce:
	$$ \lim_{\bar{b}_2 \to \infty} \Delta SC^{\bar{b}_2} =  \frac{1}{2(r+ \bar{r}(1-\bar{s})^2)} \int_0^T \lim_{\bar{b}_2 \to \infty}\left[ \left( \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} u^{\bar{b}_2}_t }{\sqrt{b_2 + \bar{b}_2}} - (b_2 + \bar{b}_2)w^{\bar{b}_2}_t \right)^2 \cdot \left(\bar{x}_t^{\bar{b}_2,MFG} \right)^2\right] dt = 0.$$	
\end{comment}

	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$. Clearly we also have $0 \leq w^{\bar{b}_2 \to \infty}_0 < \infty$. Thus,
	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV,\bar{b}_2} <\infty.$$
	Therefore, we conclude that:
	$$ \lim_{\bar{b}_2 \to \infty} PoA^{\bar{b}_2} = 1.$$
\end{proof}
